\plaintitle

### 2017-02-24 paper/paper.tex
Paper: Add abstract

% TODO abstract
\begin{abstract}
  Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
An initial study explore this questions and highlight relationship
TODO performer point of view.
TODO Initial study.
TODO proposes framework to explore performer and listeners points of view.
In addition, it explores the effect of the performer's physical effort on the audience perception and appreciation of the performance.
These questions are assessed in controlled experiment, evaluating perceived expressivity from the point of view of the performer and the listener alike.

>>>>

\begin{abstract}

  %% Intro to the field
  Computers and electronic instruments are common in music performances nowadays.
  They provide new ways of interaction and thinking about music, as well as new modes of musical expression.
  %% The problem
  On the other hand, the lack of physical effort required by these instrument can both undermine performers expressivity and the listeners understanding of the performance.
  %% One sentence of results
  My preliminary results show that users of electronic instruments prefer to have precise pitch control, even when they have to put physical effort to control it.
  They balance this requirement with the desire to have large enough pitch range.
  On the other hand users don't have strong preferences regarding amplitude control sensitivity to force.
  %% How the main results answer the problem
  The results partially support the assumption that physical effort, and by extension physical feedback from an instrument enhance controllability and therefore enable more expressivity.
  %% General context
  This findings suggest that interfaces for music performance should require physical effort from the player, as traditional instruments do, to enhance expressivity.
  %% Conclusion
